### 2020-12-16 Thesis-Chapter5-Arguments.tex
Editorial improvements

\myfig{fig-args-contrib} maps the central arguments in the EA debate. As previously stated, \ac{encryption}'s dual
contributions to information security and radical privacy are central to the debate. Of course, there is only conflict
when radical privacy is perceived as a negative. The right to privacy is both a strongly held value and an enshrined
legal principle. Many use privacy concerns to argue that \ac{EA} is socially undesirable. The Snowden revelations
\cite{landau_making_2013} unveiled the scale of privacy-eroding U.S. government surveillance enabled by technological
changes, terrorism-motivated policies, and weak oversight \cite{shamsi_2011}. Privacy violations are an abstract worry
to many, but for the most vulnerable, they are frighteningly concrete. For example, mobile phone surveillance malware
enabled the Saudi government to capture and murder journalist Jamal Khashoggi for expressing dissent against the crown
prince \cite{liebermann_2019}. At a societal level, the mere presence of surveillance changes behavior and chills free
speech \cite{rogaway_moral_2015}, and government violations of the law degrade institutional trust.

@@

Information security is the remaining central issue in the debate. As described in \mysec{sec-crypto-basics},
\ac{cryptography} plays a foundational role in nearly every aspect of security. Past \ac{EA} regulation efforts sought
to compromise the cryptographic foundations of encryption, though this is not a feature of proposals today, as that is
universally seen as too risky. \mysec{sec-tech-approaches} introduced several alternative technical approaches to
\ac{EA}, but experts still proclaim that the current state of the art is far from capable of providing the type of
access \acl{LE} in an acceptably secure manner \cite{abelson_2015} \cite{abelson_risks_1997}. Security was an
afterthought in early computing and networking designs, and the field of cybersecurity is still equal parts art and
science; mandated \ac{EA} would inevitably diminish security to some degree \cite{abelson_2015}.

Finally, it is arguable that \ac{EA} could have positive alternative applications. It could enable malware scanning,
password recovery, or administrator access in a business setting. Typically these applications have other solutions,
however, and to combine the requirements of these uses with those of any reasonable \ac{EA} proposal would likely
fatally weaken it.

@@

A significant portion of the disconnect between government and technical community representatives is disagreement over
whether law enforcement has \ii{too little} or \ii{too much} access to data. The argument for \ii{too little} is
well-represented by proponent former \ac{FBI} Director James Comey in his 2014 speech titled ``Going Dark''
\cite{comey_2014} (though he did not coin the phrase \cite{swire_encryption_2011}). The argument is presented in
\myfig{fig-arg-going-dark}.

@@

Most importantly, the ``Going Dark'' argument relies on the premise that law enforcement investigations fail due to
encryption. As described in \mysec{sed-arg-contrib}, there is no conclusive data regarding the extent to which
encryption is to blame for failed cases. One can certainly understand the argument, but the lack of evidence is an
issue. The highest-profile case of \ac{the-cw2}, Apple vs. FBI, ended when the \ac{FBI} broke into the phone and found
nothing of value. Tellingly, the examples cited in Comey's 2014 speech were not cases in which encryption inhibited
investigations, but were cases in which encryption \ii{could have} inhibited investigations, had it been a factor.
\cite{comey_2014}. More recently, a 2020 report titled ``Mass Extraction: The Widespread Power of U.S. Law Enforcement
to Search Mobile Phones'' revealed that law enforcement agencies currently have the upper hand on mobile device
encryption and are actually able to extract data from nearly every mobile phone on the market \cite{koepke_2020}.

Citing lack of evidence that encryption is stymieing cases only gets you so far, however. In most cases, it is
impossible to know what would have happened without the interference of strong encryption. Inability to gather data from
controlled tests is a characteristic of \acp{wicked-prob}. When controlled settings are unachievable, another way to
gather data is by observing naturally-occurring conditions in which everything but the variable of interest remain are
constant. These conditions exist for encryption in messaging application ecosystem. Messaging applications WhatsApp,
Facebook Messenger, and Telegram all have large user bases and similar features. Among these services, only Facebook
Messenger does not employ \ac{E2EE}. Globally, Facebook Messenger has approximately 20\% market share as measured by
active monthly users \cite{statista_2020} but accounts for 65\% of \ac{CSAM} reports \cite{keller_internet_2019}. This
indicates that encryption does indeed affect investigations.

@@

Aside from the challenge of encryption entirely, a 2018 study found that law enforcement's primary difficulties with
digital evidence were identifying service providers and getting the sought after data from them \cite{carter_2018}. This
is in the context of current legal frameworks and access capabilities. The report is fittingly titled ``Low-Hanging
Fruit,'' and also lists resource limitations and training needs among top priorities. Indeed, many current initiatives
are underfunded. Major anti-\ac{CSAM} legislation passed in 2008, but has been funded at only 50\% of authorized levels,
the Justice Department task force has produced only two of five biennial reports, and a senior executive position within
the Justice Department was never created \cite{keller_internet_2019}. Federal entities commissioned to improve
communication between law enforcement and industry as well as to train law enforcement on managing digital evidence are
similarly underfunded \cite{carter_2018}.

@@

The argument for law enforcement having \ii{too much} access to data claims that law enforcement is not ``Going Dark'';
rather, they are experiencing the ``Golden Age for Surveillance'' \cite{swire_encryption_2011}. This argument posits
that although encryption makes certain data completely unaccessible, technological change on the whole has given
authorities much more digital evidence than encryption has taken away. Paired with the dangers of \ac{masssurv},
encryption is a necessary defense, and any \ac{EA} implementation would compromise encryption's protection. The argument
is mapped in \myfig{fig-arg-golden-age}.

@@

After establishing the danger of surveillance, the argument notes how technology has increased the government's
surveillance abilities. This can hardly be contested. Going back to Comey's ``Going Dark'' examples once more, each case
he cited was cracked by digital evidence that would not have been available even twenty years ago \cite{comey_2014}. In
response to the danger of \ac{masssurv} and the scale of modern surveillance capabilities, encryption is one of the only
privacy-saving tools. (Opting out may be possible for some, but is not a realistic option for society as a whole.)

While stronger than the ``Going Dark'' argument, the ``Golden Age for Surveillance'' argument suffers from a significant
flaw. It focuses on the abilities and dangers of agencies like the \ac{NSA} while ignoring the problems of
resource-strapped local, state, and federal law enforcement. It is obvious that the amount of digital evidence is
increasing. However, law enforcement already has trouble acquiring many forms of evidence with the help of tech and
communications companies, and does not have the funding or capability to get it on its own \cite{carter_2018}.
Exacerbating the situation is the ``tech effect,'' which refers to jurors' increased expectations of hard evidence in cases
where it may be suspected to exist \cite{shelton_study_2006}.

Still, law enforcement's inability to access the tools of \ac{masssurv} cannot be taken for granted. It will likely
change---they already have access to mobile devices. A more conservative criticism of the ``Golden Age'' argument rests
in the fact that \ac{EA} without \ac{masssurv} is conceivable. \ac{EA} implementations that enable law enforcement but
thwart \ac{masssurv} by remote powers subvert most of the ``Golden Age'' argument. \ac{EA} proposals that strive for
these properties will be explored in \mysec{sec-ea-types}.

@@

Another common argument is that implementing \ac{EA}---or even researching it---inexorably moves tech policy down a
slippery slope, in which government demands will never be satisfied. This argument can be used to prevent research by
those who think judicious use of \ac{EA} tools could be positive. Going too far and too fast is certainly dangerous, but
it is both cynical and misleading to declare the permanent destruction of privacy as the inevitable end of \ac{EA}
research.

@@

The final two anti-\ac{EA} fallacies are examples of false dichotomies; they present the situation as if there are only
two options. \Acp{wicked-prob} have unlimited sets of potential responses, so reducing them to two is misleading. One
false dichotomy is that the only acceptable solutions are either perfect \ac{EA} or no \ac{EA}. This leaves no room for
risk-based approaches, the typical security strategy outside the realm of cryptography. Another false dichotomy is that
regulators must either allow strong cryptography or we will live in a \ac{masssurv} dystopia. This one carries hints of
``slippery slope'' and appeal to emotion as well, framed as a choice between only two futures. Framing the situation in
all or nothing terms reduces the chance of a successful collaborative debate.

Some arguments used to support \ac{EA} rely on appeal to emotion. Politicians and law enforcement agents often appeal to
pity for child abuse victims or fear of terrorists, drug dealers, and kidnappers to make their point. Public safety is a
central issue in the debate. The technical community does take these concerns seriously \cite{schneier_scaring_2019}.
These appeals become fallacious when they are used to manipulate the audience into supporting solutions incommensurate
with the problems or to manipulate the audience into believing that the technical community does not care about these
issues.

Another argument used to subvert anti-EA arguments from experts goes along the lines of, since we put a man on the moon,
we can surely create secure \ac{EA} \cite{cushing_moon_2018}. This is a weak analogy. The only similarity between the
challenge of landing an astronaut on the moon and the challenge of building a cryptosystem with secure EA is that they
are difficult. Once the political commitment was made, the Apollo program solved mostly tame problems and had enormous
government backing. Resolving the encryption debate has neither of these advantages. Many similar arguments comparing
\ac{EA} to other feats of technological progress suffer the same faults.

Lastly, government officials often portray \ac{EA} as a problem that security experts simply have not researched enough.
If experts just ``nerd harder,'' as some put it, they can find a solution \cite{schneier_2019}. This misses the point of
research done up to this point. Encryption and \ac{EA} is a \ac{wicked-prob} for which tame, technical-only solutions
will not work \cite{rozenshtein_wicked_2018}. Even on the technical side, experts have stated time and again that,
depending how you look at it, the technical problem is solved---\ac{EA} is easy from a purely cryptographic point of
view. The hard part is the security of the interfaces with the human users and administers of the system
\cite{abelson_risks_1997} \cite{abelson_2015}. This may not be an area of strong academic research, but to frame that
as the primary roadblock to progress utterly misses the point.

@@

Moving on from problem framing and meritless arguments, we next turn to actions that can be taken in response to the
situation. \myfig{fig-arg-measures} divides potential solutions into the categories of current capabilities, legal
measures, and \ac{EA}. Current capabilities can be implemented today, and include maintenance of the status quo and
increasing investment in current programs. Legal measures require a change in the text or application of the law, but do
not require fundamentally new technical capabilities. These include compelling passwords, which requires legal
clarification, and sanctioning lawful hacking, which requires a strategic pivot and an oversight framework. (These
non-\ac{EA} approaches were first introduced in \mysec{sec-alt-approaches}.) At this level, \ac{EA} is analyzed in
general. Specific EA approaches are addressed in the next map.

@@

Each measure is considered according to five metrics. These metrics represent a generalization of metrics from several
sources, including two separate diverse committees gathered to analyze the encryption debate
\cite{committee_decrypting_2018} \cite{group_2019} \cite{varia_2018}. They also align closely to the four central issues
of security, safety, privacy, and trust. The five metrics used to analyze response measures are (1) minimization of
increased security risk, (2) utility to law enforcement, (3) protection of civil liberties---particularly important as
after the analysis of the ``Golden Age for Surveillance'' argument---(4) transparency, and (5) economic impact. Economic
impact is not as central an issue as the others, but it does help determine practical viability of a proposal.

Beginning with current capabilities, the first choice is to do nothing. Some may conclude that the current state of
affairs actually does represent an acceptable balance of interests. If technology and government agree on this approach,
then \ac{the-cw2} can end much like the first. However, legislative action itself is a risk to be mitigated. If the
technical community ``decides'' on this approach and government continues to reject it, we could be forced in an
undesirable direction.

@@

Compelled password disclosure is a potential solution that simply requires defendants to surrender passwords and
\acp{PIN} to their devices. Questions regarding the legality of this approach have been working their way through the
courts \cite{bittenbender_2019} \cite{sobel_2019} because of the apparent conflict with the Fifth Amendment right
against self-incrimination. Even so, affordability is the strongest argument in its favor. Schneier and Kerr point out
that this approach requires the password-holder to be available to investigators, the prosecution has to overcome
several legal hurdles even if the basic approach is ruled Constitutionally legal, and even then the defendant may choose
to withhold the password and be held in contempt rather than be charged for crime evidenced by the plaintext
\cite{kerr_encryption_2017}.

\Ac{lawful-hacking} is the most prominent proposed alternative to \ac{EA} \cite{bellovin_lawful_2013}
\cite{hennessey_lawful_2016} \cite{rozenshtein_wicked_2018} \cite{kerr_encryption_2017} \cite{soesanto_2018}.
\Ac{lawful-hacking}'s support may be due in part to the fact that it is a technical approach that isn't \ac{EA} itself.
However, its effectiveness against criminals for whom \ac{EA} would not work is its obvious benefit. This is because,
while organized crime and terror groups would still use encryption tools to evade an \ac{EA} scheme, their operational
security would fail at some point, letting law enforcement or intelligence agencies into their networks and devices.
This approach is already in use \cite{cox_2020}, most famously to bring down cartel kingpin El Chapo
\cite{feuer_chapo_2019}. Because it is already used, deliberately choosing \ac{lawful-hacking} as the primary strategy
for accessing plaintext would mean officially sanctioning, formalizing, and funding \ac{lawful-hacking} programs.

Despite its strengths \ac{lawful-hacking} is a sub-optimal compromise. Because it requires time and specialized skills,
it is not useful for small departments and commonplace crimes. It would also alter the relationship between law
enforcement and tech companies. Law enforcement agencies would be forced into competition with tech companies if they
were incentivized to conceal the vulnerabilities they discover. Prominent proposals suggest mandating disclosure of
discovered vulnerabilities to mitigate this issue \cite{bellovin_lawful_2013} \cite{hennessey_lawful_2016}.
Theoretically, there are enough vulnerabilities that, even though these discovered vulnerabilities would be disclosed and
patched, new ones could be found quickly enough to enable steady levels of access. Government could source these
vulnerabilities from a combination of the public domain, the commercial exploit market, and a central ``Vulnerability
Lab'' \cite{bellovin_lawful_2013}.

@@

The final proposal is \ac{EA} itself. \ac{EA} would provide a standardized method for law enforcement to reliably access
\ac{plaintext}. It could serve as a compliment to \ac{lawful-hacking}by eliminating the incentive to conceal
vulnerabilities because it would be unnecessary for \ac{EA}-compliant systems, which would presumably include mainstream
technology. In that situation, \ac{EA} would combat common crime and \ac{lawful-hacking} would combat organized crime
and terror groups. While \ac{EA}'s impact on civil liberties and \ac{masssurv} would depend on its implementation, any
proposal would be costly to introduce and would threaten U.S. product competitiveness due to perceived insecurity. Risk
to security is the largest weakness of \ac{EA}. Any proposal must overcome significant challenges to minimize risk. The
next map analyzes this more closely.

@@

\myfig{fig-arg-classes} lists several classes of \ac{EA} and arguments in their favor and disfavor. The \ac{EA} classes
applicable to both \ac{DIM} and \ac{DAR} include weak cryptography, trusted-party key escrow, and distributed key
escrow. Using cryptographic puzzles and adding a ghost user apply to the case of \ac{DIM}, and device key escrow applies
to \ac{DAR}.

@@

% TODO: move this up? Applies to previous map as well.
It should be noted that the \ac{argmap} format works best when it displays the debate surrounding just one conclusion or
proposal. This allows adequate room for elaboration on points and counterpoints. When a map includes multiple
conclusions or proposals, it becomes a tangled web of connections, leaving no room for additional detail. For the sake
of brevity, this thesis compares several \ac{EA} variations in a single map. For an thorough discussion of \ac{EA}'s
alternatives and variations, see the National Academies of Sciences, Engineering, and Medicine's 2018 report titled
\ii{Decrypting the Encryption Debate: A Framework for Decision Makers} \cite{committee_decrypting_2018}.

The first \ac{EA} class is to simply use weak cryptographic ciphers or short encryption keys. This was the approach
taken before \ac{the-cw1}, when strong cryptography was not readily available and subjected to export controls. No party
seriously supports this approach today, as it contradicts security on many levels.

Trusted-party key escrow relies on an entity or a small group of entities to store a key or key recovery information.
There are a wide variety of implementations \cite{denning_taxonomy_1996}. This class of \ac{EA} has a crushing weakness:
it centralizes extremely sensitive information. Some argue software companies are capable of protecting such sensitive
data, citing their current practice of storing code-signing keys in hardware security modules \cite{ozzie_2018}.
However, others point out that such keys are quite rarely used (especially when compared to the likely frequency of
\ac{EA} requests), and yet they still leak \cite{green_2018}. Once the escrowed keys were stolen, as they inevitably
would be, every device or message encrypted with them would be at risk. This is an example of a case when the
\ac{argmap} format doesn't do an argument justice---the argument against any centralized access mechanism is extremely
powerful.

Distributed key escrow differs from trusted-party in that it takes strong steps to remove centralized trust. This is
achieved by using distributed systems to make key extraction difficult and publicly observable \cite{phan_key_2017}
\cite{servan_schreiber_jje_2020}. One advantage of distribution is that this approach is that it is more likely to fail
by making data unrecoverable than by making unintended data vulnerable, though more research into this area is needed.
Unfortunately, these systems would likely be costly to deploy and difficult to update due to their complexity.

One class of \ac{DIM} \ac{EA} involves using strong cryptography, but including cryptographic puzzle pieces as message
metadata. These pieces are designed to reveal the encryption key after the surveiller spends considerable computational
power \cite{bellare_translucent_1996} \cite{wright_crypto_2018}. This approach precludes mass surveillance, but it also
enables arbitrary surveillance by anyone with enough computing power. Using this class of \ac{DIM} \ac{EA} in common
cases would be impractical due to its high cost. However, it would be less effective in high-profile cases due to the
ability of sophisticated adversaries to employ \ac{EA} workarounds. Additionally, the calibration of puzzle difficulty
is dependent on the state of computing. Since opponents can record data and decrypt it later when computational
capabilities have changed, the data becomes steadily less secure over time.

Another \ac{DIM} proposal is to ``conference call'' authorities in as ghost participants in the conversation. This was
notably suggested by \ac{GCHQ} officials Ian Levy and Crispin Robinson \cite{levy_robinson_2018}. Their writeup begins
with some core ideas of this thesis:

>>>>

\myfig{fig-args-contrib} maps the central arguments in the EA debate. As previously stated, \ac{encryption}'s dual
contributions to information security and radical privacy are central to the debate. Of course, there is only conflict
when radical privacy is perceived as a negative. The right to privacy is both a strongly held value and an enshrined
legal principle. Many use privacy concerns to argue that \ac{EA} is socially undesirable. The Snowden revelations
\cite{landau_making_2013} unveiled the scale of privacy-eroding U.S. government surveillance enabled by technological
changes, terrorism-motivated policies, and weak oversight \cite{shamsi_2011}. Privacy violations are an abstract concern
to many, but for those most vulnerable, they are frighteningly concrete. For example, mobile phone surveillance malware
enabled the Saudi government to capture and murder journalist Jamal Khashoggi for expressing dissent against the crown
prince \cite{liebermann_2019}. At a societal level, the mere presence of surveillance changes behavior and suppresses
free speech \cite{rogaway_moral_2015}, and government violations of the law degrade institutional trust.

@@

Information security is the remaining central issue in the debate. As described in \mysec{sec-crypto-basics},
\ac{cryptography} plays a foundational role in nearly every aspect of security. Past \ac{EA} regulation efforts sought
to compromise the cryptographic foundations of encryption; however, this is seen as too risky today.
\mysec{sec-tech-approaches} introduced several alternative technical approaches to \ac{EA}, but experts still make clear
that current systems are incapable of securely providing the level of access \acl{LE} wants \cite{abelson_2015}
\cite{abelson_risks_1997}. Security was an afterthought in early computing and networking designs, and the field of
cybersecurity is still equal parts art and science; mandated \ac{EA} would put a heavy burden on a field still finding
its legs.
% TODO: too colloquial?

Finally, it is arguable that \ac{EA} could have positive alternative applications. It could enable malware scanning,
password recovery, or administrator access in a business setting. Typically these applications have other solutions,
however, and unnecessary requirements would weaken any \ac{EA} system.

@@

Much of the disconnect between government and the technical community is disagreement over whether law enforcement has
\ii{too little} or \ii{too much} access to data. The argument for \ii{too little} is well-represented by proponent
former \ac{FBI} Director James Comey in his 2014 speech titled ``Going Dark'' \cite{comey_2014} (though he did not coin
the phrase \cite{swire_encryption_2011}). The argument is presented in \myfig{fig-arg-going-dark}.

@@

Most importantly, the ``Going Dark'' argument relies on the premise that law enforcement investigations fail due to
encryption. As described in \mysec{sed-arg-contrib}, there is no conclusive data regarding the extent to which
encryption is to blame for failed cases. The highest-profile case of \ac{the-cw2}, Apple vs. FBI, ended when the
\ac{FBI} broke into the phone and found nothing of value. Tellingly, the examples cited in Comey's 2014 speech were not
cases in which encryption inhibited investigations, but were cases in which encryption \ii{could have} inhibited
investigations, had it been a factor. \cite{comey_2014}. More recently, a 2020 report titled ``Mass Extraction: The
Widespread Power of U.S. Law Enforcement to Search Mobile Phones'' revealed that current hacking tools are stronger than
mobile device encryption's defenses, and law enforcement is actually able to extract data from nearly every mobile phone
on the market \cite{koepke_2020}. Without conclusive data showing the extent that encryption hinders investigations, the
``Going Dark'' argument weakens.

Lack of evidence for an argument does not prove that it is incorrect. Because law enforcement has the data, the burden
of proof lies with them to show that encryption is causing investigatory failure. However, in most cases, it is
impossible to know what would have happened without the interference of strong encryption. Inability to gather data from
controlled tests is a characteristic of \acp{wicked-prob}. When controlled settings are unachievable, another way to
gather data is by observing naturally-occurring conditions in which everything but the variable of interest remain are
constant. These conditions exist for encryption in messaging application ecosystem. Messaging applications WhatsApp,
Facebook Messenger, and Telegram all have large user bases and similar features. Among these services, only Facebook
Messenger does not employ \ac{E2EE}. Globally, Facebook Messenger has approximately 20\% market share as measured by
active monthly users \cite{statista_2020} but accounts for 65\% of \ac{CSAM} reports \cite{keller_internet_2019}. This
indicates that encryption does indeed affect investigations.

@@

Encryption is not the only challenge that law enforcement faces with digital evidence. A 2018 study found that
identifying service providers and getting data from them using existing mechanisms were even greater impediments
\cite{carter_2018}. The report, titled ``Low-Hanging Fruit,'' also lists resource limitations and poor training as top
issues. Indeed, many current initiatives are underfunded. The \ii{New York Times}' 2019 investigation into \ac{CSAM}
found chronic lack of commitment from government initiatives---major legislation passed in 2008, but has been funded at
only 50\% of authorized levels; a commissioned Justice Department task force has produced only two of five biennial
reports; and a senior executive position within the Justice Department to target \ac{CSAM} was never created
\cite{keller_internet_2019}. Federal entities aiming to improve training and coordination between law enforcement and
industry are similarly underfunded \cite{carter_2018}.

@@

The argument for law enforcement having \ii{too much} access to data claims that law enforcement is not ``Going Dark'';
rather, they are experiencing the ``Golden Age for Surveillance'' \cite{swire_encryption_2011}. This argument posits
that although encryption makes certain data completely unaccessible, technological change on the whole has given
authorities much more digital evidence than encryption has taken away. Paired with the dangers of \ac{masssurv},
encryption is a necessary defense. \Ac{EA} would compromise encryption's defense against \ac{masssurv}, and must
therefore be opposed. The argument is mapped in \myfig{fig-arg-golden-age}.

@@

After establishing the danger of surveillance, the argument notes how technology has increased the government's
surveillance abilities. This statement as strong evidence. In Comey's ``Going Dark'' speech, it was digital evidence
which would not have existed twenty years ago that cracked each case \cite{comey_2014}. Encryption is one of the only
privacy-saving technologies to emerge alongside the boom in privacy-eroding technologies. Opting out of the
technological boom is possible for some, but is not a realistic option for society as a whole. Due to the dangers of
\ac{masssurv}, \ac{encryption} must be embraced.

While stronger than the ``Going Dark'' argument, the ``Golden Age for Surveillance'' argument suffers from a significant
flaw. It focuses on the abilities and dangers of agencies like the \ac{NSA} while ignoring the problems of
resource-strapped local, state, and federal law enforcement. It is obvious that the amount of digital evidence is
increasing. However, as seen in ``Going Dark'' argument, law enforcement has considerable struggles with digital
evidence, even aside from encryption. Exacerbating the problem for justice system is the ``tech effect,'' which refers
to jurors' increased expectations of digital evidence in cases where they suspect it exists \cite{shelton_study_2006}.

Still, law enforcement's inability to access the tools of \ac{masssurv} cannot be taken for granted. It will likely
change---they already have access to mobile devices. A more conservative criticism of the ``Golden Age'' argument rests
in the fact that \ac{EA} without \ac{masssurv} is conceivable. \ac{EA} implementations that enable law enforcement while
thwarting \ac{masssurv} subvert most of the ``Golden Age'' argument. \ac{EA} proposals with these aims will be explored
in \mysec{sec-ea-types}.

@@

Another common argument is that implementing \ac{EA}---or even researching it---inexorably moves tech policy down a
slippery slope, in which government demands will never be satisfied. This argument can be used to prevent anyone from
seeking a middle ground. Going too far and too fast is certainly dangerous, but it is both cynical and misleading to
declare the permanent destruction of privacy as the inevitable end of \ac{EA} research.

@@

The final two anti-\ac{EA} fallacies are examples of false dichotomies; they present the situation as if there are only
two options. \Acp{wicked-prob} have unlimited sets of potential responses, so reducing them to two is misleading.
Holding either perfect \ac{EA} or no \ac{EA} at all as the only acceptable solutions is one false dichotomy. This leaves
no room for risk-based approaches, the typical security strategy outside the realm of cryptography. Suggesting that
regulators must either allow strong cryptography or we will live in a \ac{masssurv} dystopia is another false dichotomy.
This leans towards ``slippery slope'' and appeal to emotion fallacies as well. Framing the situation in all or nothing
terms reduces the chance of a successful collaborative debate.

Some arguments used to support \ac{EA} rely on appeal to emotion. Politicians and law enforcement agents often argue for
\ac{EA} by appealing to pity for child abuse victims or appealing to fear of terrorists, drug dealers, and kidnappers.
Public safety is a central issue in the debate. The technical community does take these concerns seriously
\cite{schneier_scaring_2019}. These appeals become fallacious when they are used to manipulate the audience into
supporting solutions incommensurate with the problems or to manipulate the audience into believing that the technical
community does not care about these issues.

When experts argue against \ac{EA} due to security challenges, some respond that since we put a man on the moon, we can
surely create secure \ac{EA} \cite{cushing_moon_2018}. This is a weak analogy. The only similarity between the challenge
of landing an astronaut on the moon and the challenge of building a cryptosystem with secure EA is that they are
difficult. Once the political commitment was made, the Apollo program solved mostly tame problems and had enormous
government backing. Resolving the encryption debate has neither of these advantages. Many similar arguments comparing
\ac{EA} to other feats of technological progress suffer the same faults.

Lastly, government officials often portray \ac{EA} as a problem that security experts simply have not researched enough.
If experts just ``nerd harder,'' as some put it, they can find a solution \cite{schneier_2019}. Concluding that
encryption policy can be settled merely by more technical research misses the point of the research done up to this
point. Encryption policy is a \ac{wicked-prob} for which tame, technical-only solutions will not work
\cite{rozenshtein_wicked_2018}. Even on the technical side, research has concluded that, depending how you look at it,
the technical problem is solved. \Ac{EA} is easy from a purely cryptographic point of view; the interfaces between the
cryptographic and human portions of the system pose the real difficulty \cite{abelson_risks_1997} \cite{abelson_2015}.
This may not be an area of strong academic inquiry, but to frame lack of technical research as the primary roadblock to
encryption policy progress utterly misses the point.

@@

Previous maps have framed the debate, presented leading arguments, and called-out fallacious arguments. The next map
explores potential solutions. \myfig{fig-arg-measures} divides potential solutions into the categories of current
capabilities, legal measures, and \ac{EA}. Current capabilities can be implemented today, and include maintenance of the
status quo and increasing investment in current programs. Legal measures require a change in the text or application of
the law, but do not require fundamentally new technical capabilities. These include compelling passwords, which requires
legal clarification, and sanctioning lawful hacking, which requires a strategic pivot and an oversight framework. (These
non-\ac{EA} approaches were first introduced in \mysec{sec-alt-approaches}.) In this section, \ac{EA} is compared to its
alternatives. \ac{EA} variations are compared in the next map.

It should be noted that the \ac{argmap} format works best when it displays the debate surrounding just one conclusion or
proposal. This allows adequate room for elaboration on points and counterpoints. When a map includes multiple
conclusions or proposals, it becomes a tangled web of connections, leaving no room for additional detail. For the sake
of brevity, this thesis compares \ac{EA}'s alternatives and variations in single maps. For a thorough discussion of both
\ac{EA}'s alternatives and variations, see the National Academies of Sciences, Engineering, and Medicine's 2018 report
titled \ii{Decrypting the Encryption Debate: A Framework for Decision Makers} \cite{committee_decrypting_2018}.

@@

In \myfig{fig-arg-measures}, response measures are considered according to five metrics. These metrics represent are
based on several sources, including two separate diverse committees gathered to analyze the encryption debate
\cite{committee_decrypting_2018} \cite{group_2019} \cite{varia_2018}. They also align closely to the four central issues
of security, safety, privacy, and trust. The five metrics used to analyze response measures are (1) minimization of
increased security risk, (2) utility to law enforcement, (3) protection of civil liberties---particularly important as
after the analysis of the ``Golden Age for Surveillance'' argument---(4) transparency, and (5) economic impact. Economic
impact is not as central an issue as the others, but it does help determine practical viability of a proposal.

Potential solutions are divided into the categories of current capabilities, legal measures, and exceptional access. The
first option, in the category of current capabilities, is to do nothing. Some may conclude that the current state of
affairs actually does represent an acceptable balance of interests. If technology and government agree on this approach,
then \ac{the-cw2} can end much like the first. However, legislative action itself is a risk to be mitigated. If the
technical community settles on this approach and government continues to reject it, the government could force its will
and move encryption policy in a dangerous direction.

@@

Compelled password disclosure is a potential solution that simply requires defendants to surrender passwords and
\acp{PIN} to their devices. Questions regarding the legality of this approach have been working their way through the
courts \cite{bittenbender_2019} \cite{sobel_2019} because of the apparent conflict with the Fifth Amendment right
against self-incrimination. Affordability is the strongest argument in compelled password disclosure's favor. Schneier
and Kerr point out several weaknesses with this approach: prosecution must overcome the aforementioned legal hurdles,
the password-holder must be available to investigators, and the password-holder must choose to provide the password
rather than be held in contempt of court \cite{kerr_encryption_2017}. Being found in contempt of court would often be
preferable to conviction of the original crime.

\Ac{lawful-hacking} is the most prominent proposed alternative to \ac{EA} \cite{bellovin_lawful_2013}
\cite{hennessey_lawful_2016} \cite{rozenshtein_wicked_2018} \cite{kerr_encryption_2017} \cite{soesanto_2018}.
\Ac{lawful-hacking}'s support may be due in part to the fact that it is a technical approach that isn't \ac{EA} itself.
However, its effectiveness against criminals for whom \ac{EA} would not work is its obvious benefit. This is because,
while organized crime and terror groups would still use encryption tools to evade an \ac{EA} scheme, their operational
security would fail at some point, letting law enforcement or intelligence agencies into their networks and devices.
This approach has already been used \cite{cox_2020}, most famously to bring down cartel kingpin El Chapo
\cite{feuer_chapo_2019}. Because it is already used, using \ac{lawful-hacking} as the primary strategy would require
officially sanctioning, formalizing, and funding \ac{lawful-hacking} programs.

Despite its strengths, \ac{lawful-hacking} is a sub-optimal compromise. Because it requires time and specialized skills,
it is not useful for small departments and commonplace crimes. It would also alter the relationship between law
enforcement and tech companies. Law enforcement agencies would be forced into competition with tech companies if they
were incentivized to conceal the vulnerabilities they discover. Prominent proposals suggest mandating disclosure of
discovered vulnerabilities to mitigate this issue \cite{bellovin_lawful_2013} \cite{hennessey_lawful_2016}.
Theoretically, there are enough vulnerabilities that, even though these discovered vulnerabilities would be disclosed and
patched, new ones could be found quickly enough to enable steady levels of access. Government could source these
vulnerabilities from a combination of the public domain, the commercial exploit market, and a central ``Vulnerability
Lab'' \cite{bellovin_lawful_2013}.

@@

The final proposal is \ac{EA} itself. \ac{EA} would provide a standardized method for law enforcement to reliably access
\ac{plaintext}. It could compliment \ac{lawful-hacking}by eliminating the incentive to conceal vulnerabilities, because
hacking would be unnecessary for \ac{EA}-compliant systems. If used together, \ac{EA} would combat common crime and
\ac{lawful-hacking} would combat organized crime and terror groups. \Ac{EA}'s impact on civil liberties and
\ac{masssurv} would depend on its implementation. Any proposal would be costly to deploy and would threaten U.S. product
competitiveness due to perceived insecurity. Increased security risk is the largest weakness of \ac{EA}. Any proposal
must overcome significant challenges to minimize risk. The next map analyzes this more closely.

@@

\myfig{fig-arg-classes} maps the arguments surrounding several classes of \ac{EA}. Weak cryptography, trusted-party key
escrow, and distributed key escrow apply to both \ac{DAR} and \ac{DIM}. Device key escrow applies only to \ac{DAR}, and
cryptographic puzzles and ghost users apply only to \ac{DIM}.

@@

The first type of \ac{EA} is simply use of weak cryptographic ciphers or short encryption keys. This was the approach
taken before \ac{the-cw1}, when strong cryptography was not readily available and was subjected to export controls. No
party seriously supports this approach today, as far too many attackers would have the capability to abuse it.

Trusted-party key escrow relies on an entity or a small group of entities to store a key or key recovery information.
There are a wide variety of implementations from the days of \ac{the-cw1} \cite{denning_taxonomy_1996}. This type of
\ac{EA} has a crushing weakness: it centralizes extremely sensitive information, which results in high risk. Some argue
software companies are capable of protecting such sensitive data, citing their current practice of storing code-signing
keys in \acp{HSM} \cite{ozzie_2018}. However, such keys are rarely used in comparison to \ac{EA} keys, which would be
updated and accessed frequently. Despite code-signing keys being rarely used and protected in \acp{HSM}, they they still
leak \cite{green_2018}. Once the escrowed keys leak, every device or message encrypted with them would be at risk. This
is a case where the \ac{argmap} format fails to reflect an argument's strength---the argument against any centralized
access mechanism is powerful.

Distributed key escrow differs from trusted-party in that it takes strong steps to remove centralized trust. This is
achieved by using distributed systems to make key extraction difficult and publicly observable \cite{phan_key_2017}
\cite{servan_schreiber_jje_2020}. One advantage of distribution over centralization is that it is more likely to fail
safely. System failure would more likely result in \ii{no one} to be able to recover plaintext instead of \ii{anyone}.
More research in this area is needed. Unfortunately, these systems would likely be costly to deploy and difficult to
update due to their complexity.

One type of \ac{DIM} \ac{EA} involves using strong cryptography, but including cryptographic ``puzzle pieces'' in
message metadata. A surveiller could reconstruct the encryption key from the puzzle pieces, but only after expending
considerable computational power \cite{bellare_translucent_1996} \cite{wright_crypto_2018}. This approach precludes mass
surveillance, but it also enables arbitrary surveillance by anyone with enough computing power. Using this type of
\ac{DIM} \ac{EA} in common cases would be impractical due to its high cost. However, it would be less effective in
high-profile cases due to the ability of sophisticated adversaries to employ \ac{EA} workarounds. Additionally, puzzle
difficulty would be calibrated based on ever-changing standards of computational capabilities. Since opponents can
record data and decrypt it later when capabilities have changed, the data becomes steadily less secure over time.

Another \ac{DIM} \ac{EA} proposal involves adding authorities as a ``ghost'' participant in a conversation, analogous to
a silent listener on a conference call. This was notably suggested by \ac{GCHQ} officials Ian Levy and Crispin Robinson
\cite{levy_robinson_2018}. Their writeup is based on the same foundational principles as this thesis:
